---
title: "Quarto Manuscript Template"
author:
  - name: "Your Name"
    orcid: 0000-0000-0000-0000
    email: your.email@example.com
    corresponding: true
    affiliations:
      - name: Your Institution
        department: Your Department
        city: Your City
        state: Your State
        country: Your Country
abstract: |
  This is a template for creating manuscripts with Quarto. Replace this
  abstract with your own summary of the work: the research question,
  methods, key findings, and conclusions. Aim for 150--250 words for
  most journals.
keywords:
  - template
  - quarto
  - manuscript
---

# Introduction {#sec-intro}

This is a Quarto manuscript template. The manuscript is available in
multiple formats:

- **HTML**: An interactive web version with table of contents and
  linked cross-references
- **PDF**: A print-ready document suitable for journal submission
- **DOCX**: A Microsoft Word document for collaborators who prefer
  tracked changes
- **JATS XML**: A structured format required by some journals and
  preprint servers

Cite references with `@citationkey` [@example2024] or in parentheses
[@example-article2024].

## Background

Add background and motivation here. Cross-reference sections with
`@sec-methods` (renders as @sec-methods).

# Methods {#sec-methods}

Describe your study design, data sources, and analysis approach here.

## Data

You can include inline R code: the square root of 2 is
`r round(sqrt(2), 4)`.

## Analysis

Code chunks execute and embed results:

```{r}
#| label: tbl-summary
#| tbl-cap: "Example summary statistics."
summary(mtcars[, c("mpg", "wt", "hp")])
```

Supplementary analyses live in a separate notebook
(`notebooks/supplementary-analysis.qmd`) and are embedded in the HTML
output automatically.

# Results {#sec-results}

Present your findings here. Reference figures with `@fig-example`
(@fig-example) and tables with `@tbl-summary` (@tbl-summary).

```{r}
#| label: fig-example
#| fig-cap: "Fuel economy vs. weight for 32 cars."
#| fig-alt: "Scatter plot showing a negative relationship between car
#|   weight (x-axis) and fuel economy in miles per gallon (y-axis)."
library(ggplot2)
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(x = "Weight (1000 lbs)", y = "Fuel economy (mpg)") +
  theme_minimal()
```

# Discussion {#sec-discussion}

Interpret your results, address limitations, and describe implications.

# Conclusion {#sec-conclusion}

Summarize the key findings and their significance.

# References {.unnumbered}

::: {#refs}
:::
